\subsection{Approach}
The general algorithm is to take first determine the relationship $a(q)$ using the simplified equation. Using this relationship we can also decide a reasonable interval for $q$. We then use the lower and upper bound for $a$ as our starting guesses for $q$ and calculate $a$ for every $q$. We then use these values to calculate the arc length and if it is satisfyingly close to 0.5 we have found our values for $q$ and $a$. If it is not we guess a new value for $q$.

This approach is the one we found worked best. We also tried two other approaches that are mentioned in the discussion.

\subsection{Simplified equation}
When we consider the equation at $x=0$ we can omit the $y'$ term. We are given a possible solution $y(x)=0.3*cos(\sqrt{q}*x)$. To prove this is correct we do the following:

\begin{center}
    \input{equations/y_proof.tex}
\end{center}

This in turn gives us the relationship $a(q)$:

\begin{center}
    \input{equations/a_q_relation.tex}
\end{center}

It follows that:

\begin{center}
    \input{equations/q_a_relation.tex}
\end{center}

\subsection{Interval for q}
Using the pythagorean theorem, we can conclude that the upper bound for $a$ can be calculated as:

\begin{center}
    \input{equations/a_upper_bound.tex}
\end{center}


The concave function representing the bow will have a longer arc length than the linear function intersecting the x-axis at the same x-value for any given $x$ within our constraints. An upper bound of $0.4$ for $a$ means the lower value for $q$ is $15.4$.

For the lower bound of $a$ we simply use 0. Since the lower bound for $a$ is used to calculate the upper bound of $q$ this does not matter a whole lot. We expect to find our value for $a$ closer to the upper bound rather than the lower.

<<<<<<< bd5bf440230d789c9a60b2b71ecd44fb578d00c7
\subsection{Arc Length}
Starting at $q=0$ we calculate $a(q)$ and $arcLength(q, a(q))$. If $abs(arcLength(q, a(q))-0.5) < 1.e-5$ we terminate our algorithm since we have found the sought precision of the arc length. If the condition is not met we increment $q$ by 0.001 and start over.
=======
\subsection{Arc length}
Starting at $q=0$ we calculate $a(q)$ and $arcLength(q, a(q))$. If $abs(arcLength(q, a(q))-0.5) < 1.e-5$ we terminate our algorithm since we have found the sought precision of the arc length. If the condition is not met we increment $q$ by 0.001 and start oer.
>>>>>>> update report to conform to specifications

\subsection{Force acting upon the bow}
Since the lever arm is 0.3 we get a trivial equation:

\begin{center}
    \input{equations/force.tex}
\end{center}
